\documentclass{article}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage[parfill]{parskip}
\usepackage{ragged2e}
\usepackage{hyperref}
\usepackage[top = 3in,headsep=30pt]{geometry}
\usepackage{fancyhdr}
\usepackage{tikz}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields


\lhead{
\textbf{Omkar Milind Nitsure} \\
\textbf{210070057} \\
Pursuing Honours in Electrical Engineering}

\rhead{\textbf{CPI: XX.XX}\\
2nd Year UG Btech student \\
DOB : 05/02/2003}

\lfoot{Indian Institute of Technology, Bombay}

\rfoot{Page \thepage}

\renewcommand{\footrulewidth}{1pt}


\begin{document}

\section*{\color{blue!60!black}ACADEMIC ACHIEVEMENTS:}

\begin{itemize}
    \item Received both Primary and Secondary Scholarships from Government of Maharashtra.
    \item Awarded with \textit{\textbf{Silver}} and \textit{\textbf{Bronze}} medals in Homi Bhabha Exam in 6th and 9th std.
    \item Honoured with \textbf{\textit{Certificate of Excellence in Mathematics}} from IPM for 6 years.
    \item Matriculation: \textbf{97.6} \verb!%! , HSC: \textbf{93} \verb!%! \hfill{(2019 and 2021)}
    \item Selected in \textbf{\textit{top 100}} students in National Physics Olympiad.  \hfill{(2021)}
    \item Selected in \textbf{\textit{top 150}} students in National Mathematics Olympiad.  \hfill{(2021)}
    \item Selected in \textbf{\textit{top 300}} students in National Chemistry Olympiad.  \hfill{(2021)}
    \item \textbf{AIR 120} in JEE Mains 2021. \hfill{(2021)}
    \item \textbf{AIR 275} in JEE Advanced 2021. \hfill{(2021)}
    \item Currently pursuing \textbf{\textit{Minor in Artificial Intelligence and Data Science.}}
\end{itemize}

\begin{tikzpicture}
\draw (0,0)--(15,0);
\end{tikzpicture}

\section*{\color{blue!60!black}ACADEMIC PROJECTS:}


\begin{itemize}
    \item \textbf{LEARNER'S SPACE: } \hfill{(2022)}\begin{itemize}
        \item \LaTeX{}
        \item Web Development
        \item Control Systems
        \item Introduction to Blockchain
        \item Tinkering Bootcamp
        \item Entering Financial Markets
    \end{itemize}
    \item \textbf{Personal Projects: }\begin{itemize}
        \item Ball On a Plate, \textbf{\textit{Control Systems}} \hfill{(2022)}
        \item Shooting Balls Game in \textbf{\textit{CS101}} \hfill{(2021)}
        \item Created my own locally hosted website  \hfill{(2022)}
    \item Participated in robot fighting event of Techfest,IIT Bombay \hfill{(2016)}
    \end{itemize}
\end{itemize}

\newgeometry{}

\thispagestyle{fancy}

\fancyhf{}

\lhead{Omkar Milind Nitsure}

\rhead{210070057}

\lfoot{Indian Institute of Technology, Bombay}

\rfoot{Page \thepage}

\section*{\color{blue!60!black}Science Experimental Project: }


\begin{itemize}
    \item Created a basic chess Engine which allowed for human vs human gameplay,\textbf{throws an error at illegal moves, }in accordance with the rules. \hfill{(2018)}
    \item Developed the control model of an inverted pendulum using Matlab and executed it in experience. \hfill{(2022)}
    \item Developed a mini-robot for the School Science Exhibition. \hfill{(2017)}
\end{itemize}

\begin{tikzpicture}
\draw (0,0)--(15,0);
\end{tikzpicture}

\section*{\color{blue!60!black}TECHNICAL SKILLS:}


\begin{itemize}
    \item \textbf{Languages: }C/C++, Python, Java, Bash
    \item \textbf{Softwares: }Git, \LaTeX{}, Matlab, Autocad, Solidworks, Android SDK, GNU octave
    \item \textbf{Development: }HTML, CSS, Javascript, Django, Angular
    \item \textbf{Key Courses: }Data structures and Algorithms + Lab, Quantum Information and Computing, Logic for Computer Science, Probability and Random Processes, Microprocessors, Control System + Lab, Electronics Design Lab, Operating Systems + Lab
\end{itemize}

\begin{tikzpicture}
\draw (0,0) -- (15,0);
\end{tikzpicture}

\section*{\color{blue!60!black}EXTRACURRICULAR ACTIVITIES:}

\begin{itemize}
    \item Awarded with \textbf{A} grade in Elementary Drawing Competition. \hfill{(2016)}
    \item Awarded with \textbf{B} grade in Intermediate Drawing Competition.\hfill{(2017)}
    \item Captained the school Table-Tennis team for 3 consecutive years in Interschool competitions.
    \item Honoured as District Table-Tennis chaampion for 4 years.
    \item Appointed as \textbf{Head Boy,Saraswati Secondary School} \hfill{(2019)}
\end{itemize}

\begin{tikzpicture}
\draw (0,0) -- (15,0);
\end{tikzpicture}

\end{document}